Accuracy and precision of zero-heat-flux temperature monitoring

### 2019-11-26 manuscript/manuscript.Rmd
manuscript in distill format

---
title: "Accuracy and precision of zero-heat-flux temperature monitoring: a systematic review and meta-analysis"
titlerunning: Accuracy of zero-heat-flux temperature monitoring
authorrunning: Conway
thanks: | 
    Grants or other notes about the article that should go on the front 
    page should be placed here. General acknowledgments should be placed at the
    end of the article.

authors: 
- name: Aaron Conway
  address: Peter Munk Cardiac Centre, UHN & Lawrence S. Bloomberg Faculty of Nursing, University of Toronto
  email: aaron.conway@utoronto.ca
- name: Navpreet Kamboj
  address: Lawrence S. Bloomberg Faculty of Nursing, University of Toronto
  email: navpreet.kamboj@mail.utoronto.ca

keywords:
- key
- dictionary
- word

abstract: |
  The text of your abstract.  150 -- 250 words.

bibliography: bibliography.bib
output: rticles::springer_article
---

```{r echo=FALSE, include=FALSE}
library(tidyverse)
library(kableExtra)
library(qwraps2)
library(knitr)
library(bama)
```

```{r load-data, include=FALSE}
data <- readxl::read_xlsx(here::here("data", "zhf_extracted.xlsx"))
```

@@

# Introduction

@@

# Methods

@@

## Inclusion criteria

@@

## Data sources and searches

Published studies were found by searching Medline and EMBASE from January 2000 to July 2019. The Cochrane-recommended search strategy combining terms for the ‘target condition’ and ‘index test’ was used [@mann2012should]. This search strategy is an efficient approach for systematic reviews of diagnostic test accuracy studies.[@preston2015improving] We also conducted forward citation searching, by using Google Scholar to search the citations of the first article published on the accuracy of zero-heat-flux thermometers. The search strategies used for each data base can be located [here](shiny app). Selection of studies was undertaken independently by two reviewers using [Covidence](https://www.covidence.org).

## Data extraction and quality assessment

@@

## Data synthesis and analysis

@@

Measures of uncertainty were included in our meta-analyses by calculating the outer $95\%$ confidence intervals for pooled limits of agreement. We also accounted for repeated measurements if they were not properly adjusted for in individual studies. This was achieved by using weights proportional to the number of participants, not the total number of measurements.  The R statistical program was used to conduct all analyses [@team2017r]. All data and R code used in the meta-analyses can be located [here]().

Prior to conducting the meta-analyses, the results from each study were converted into a standard format, with bias meaning $comparator thermometer-ZHF thermometer$ measured in $^\circ C$. In several studies, results were reported for multiple groups of participants, therefore in the meta-analysis each of these groups was treated as a separate 'comparison'. Other studies reported multiple sets of results, whereby analyses were conducted between ZHF and various comparator devices used on the same participant. These instances were also treated as a separate 'comparison' if the comparator devices were apart of separate meta-analyses groups. One study reported intraoperative, postoperative and overall results for the same participants. Only the paired measurements from the overall results were included in the main and low risk bias analyses, leaving paired measurements exclusively from the intraoperative and postoperative timepoints to be included in respective meta-analyses subgroups.

The conventionally cited clinically acceptable agreement between ZHF and comparator devices is 0.5 $^\circ C$ $(ref - most of the studies site this range from Eshragi...)$. It was deemed that outer confidence bounds for 95% LoA between zero-heat-flux and core temperature measurements (termed as ‘population limits of agreement’) outside of these bounds wouldbe clinically unacceptable.

A sensitivity analysis for the primary comparison (ZHF versus temperature measurement at core site) was performed based on risk of bias, whereby ‘unclear risk of bias’ was treated as ‘high risk’ and ‘high risk of bias’ studies were excluded from analyses. As clinicians would be interested in the accuracy of ZHF relative to the thermometer devices they use, and within the clinical setting in which they use it, we conducted subgroup analyses according to the comparator device used (either core, sublingual or nasopharangeal) and clinical setting (either intraoperative or intensive care unit).

# Results

## Study selection and description

Fifteen studies were included (Figure 1). Two studies reported only in abstract form were not included and assigned as 'studies awaiting classification' because there was insufficient information provided.

@@

The characteristics of included studies can be viewed [here](link to shiny app). The primary comparison of zero-heat-flux versus core temperature measurements (eg, arterial, bladder, esophageal or rectal) consisted of `r primary$Comparisons` comparisons from `r primary$Studies` individual studies. In total, data from `r primary$Participants` participants with `r format(primary$Measurements, scientfic=F)` paired measurements were included in this comparison (two studies did not report the total number of measurements included in their analysis). The sensitivity analysis for the primary comparison with only studies that were judged as low risk of bias across all domains included `r low_risk$Comparisons` comparisons from `r low_risk$Studies` studies that enrolled `r low_risk$Participants` participants with `r low_risk$Measurements` paired measurements (two studies did not report the total number of measurements included in their analysis). There were `r ICU$Studies` studies that compared zero-heat-flux to core temperature measurements in ICU patients, comprising `r ICU$Comparisons` comparisons with `r ICU$Measurements` measurements from `r ICU$Participants` participants. Another `r OT$Studies` studies were included that compared zero-heat-flux to core temperature measurements in patients undergoing surgery, comprising `r OT$Comparisons` comparisons with `r OT$Measurements` measurements from `r OT$Participants` participants. Nasopharyngeal thermometers were used as the comparator devices in `r NPA$Studies` studies, with `r NPA$Measurements` paired measurements from `r NPA$Measurements` participants. Sublingual thermometers were used as the comparator devices in `r SL$Studies` studies that reported `r SL$Measurements` paired measurements from `r SL$Participants` participants.

@@

## Primary comparison: zero-heat-flux thermometer versus core thermometers

The pooled estimate for the mean bias between zero-heat-flux and core temperature measurements was `r primary$bias_mean`$^\circ C$. However, the variation in differences between studies was large, as displayed by the density plot in Figure 2. Consequently, the population limits of agreement, which take into consideration the between-study heterogeneity and sampling error, were wide, spanning from `r primary$CI_L_rve`$^\circ C$ to `r primary$CI_U_rve`$^\circ C$ (`r primary$Measurements` measurements; `r primary$Participants` participants; `r primary$Studies` studies). The quality of evidence for the primary comparison was downgraded to low quality due to concerns about study limitations and inconsistency. Population limits of agreement for the sensitivity analysis restricted to studies rated as having low risk of bias across all the domains of the QADAS-2 were similar to the primary analysis (`r low_risk$Measurements` measurements; `r low_risk$Participants` participants; `r low_risk$Studies` stsudies). The mean bias was again `r low_risk$bias_mean`$^\circ C$ with population agreements spanning from `r low_risk$CI_L_rve`$^\circ C$ to `r low_risk$CI_U_rve`$^\circ C$.

```{r fig-2, fig.align="center", fig.cap="Comparisons between core and zero-heat-flux thermometers within and across studies. Blue curves are distributions of the differences between measurements from zero-heat-flux (ZHF) sensors and core temperature measurements in individual studies. The red curve is the distribution of the pooled estimate.", echo=FALSE, fig.width=5.1, fig.path=""}

    bias=data_core$bias
    s2_unb = data_core$s2
    pooled_bias = primary$bias_mean
    pooled_sd = primary$sd2_est
    pooled_tau2 = primary$tau_est
    pooled_sd = sqrt(pooled_sd^2 + pooled_tau2)

    LOA_l = primary$LOA_L
    LOA_u = primary$LOA_U
    LOA_l_CI = primary$CI_L_rve
    LOA_u_CI = primary$CI_U_rve

g <- ggplot(data.frame(x=seq(-20,20,length=200)), aes(x=x)) + 
      stat_function(fun=dnorm, args = list(bias[1], sd=sqrt(s2_unb[1])), colour = "cornflowerblue", size=0.6, alpha = 0.5)

    for (i in 2:length(bias)){
      g <- g + stat_function(fun=dnorm, args = list(bias[i], sd=sqrt(s2_unb[i])), color = "cornflowerblue", size = 0.6, alpha = 0.5)
    }

    g <- g + stat_function(fun=dnorm, args = list(pooled_bias, pooled_sd), colour ="lightcoral", alpha = 0.05) + 
      stat_function(fun=dnorm, args = list(pooled_bias, pooled_sd), colour = NA, geom="area", fill="lightcoral", alpha = 0.6) + 
      scale_x_continuous(limits = c(-3.5,3.5), breaks = c(-2, -1, 0, 1, 2)) + labs(x = expression('Difference between core and ZHF temperature measurements in'*~degree*C*''))+
      scale_y_continuous(name = "Density \n", limits = c(0,2.5)) +  
      #labs(title = "\nOuter confidence intervals for pooled limits of agreement\n\n  Pooled limits of agreement")+
      theme(plot.title = element_text(hjust = 0.5, margin = margin(t=10, b=-32), size=10),
            axis.text=element_text(hjust = 0.5, size=10),                                                                        
            axis.title=element_text(hjust = 0.5, size=10),
            axis.line=element_line(colour="black", size=0.2),
            panel.background = element_blank(),
            axis.ticks = element_blank(), 
            plot.caption = element_text(hjust = 0)) #+ 
      #CI lines that extend to arrow tips
      # geom_segment(aes(x=LOA_u, y=0, xend=LOA_u, yend=2.25), size = 0.3, linetype="dashed")+ 
      # geom_segment(aes(x=LOA_l, y=0, xend=LOA_l, yend=2.25), size = 0.3, linetype="dashed")+
      # geom_segment(aes(x=LOA_u_CI, y=0, xend=LOA_u_CI, yend=2.48), size = 0.3)+
      # geom_segment(aes(x=LOA_l_CI, y=0, xend=LOA_l_CI, yend=2.48), size = 0.3)#+
      # 
      # geom_segment(aes(x=0, y=2.48, xend=LOA_u_CI, yend=2.48), size = 0.4, arrow = arrow(length = unit(0.03, "npc")))+ #R arrow high
      # geom_segment(aes(x=0, y=2.48, xend=LOA_l_CI, yend=2.48), size = 0.4, arrow = arrow(length = unit(0.03, "npc")))+ #L arrow high
      # geom_segment(aes(x=0, y=2.25, xend=LOA_u, yend=2.25), size = 0.4,  arrow = arrow(length = unit(0.03, "npc")))+ #R arrow low
      # geom_segment(aes(x=0, y=2.25, xend=LOA_l, yend=2.25), size = 0.4,  arrow = arrow(length = unit(0.03, "npc"))) #L arrow low
g
```

We conducted two subgroup analyses for the primary comparison according to the clinical setting in which the study was conducted. In the subset of studies conducted in the ICU, the mean bias was `r ICU$bias_mean` $^\circ C$ with population limits of agreement between `r ICU$CI_L_rve` $^\circ C$ and `r ICU$CI_U_rve` $^\circ C$. Whereas in the subset of studies that evaluated the use of zero-heat-flux thermometers during surgery found a mean bias of `r OT$bias_mean` $^\circ C$ with population limits of agreement from `r OT$CI_L_rve` $^\circ C$ to `r OT$CI_U_rve` $^\circ C$. The quality of evidence for these subgroup analyses was similarly rated as low quality due to concerns about study limitations and inconsistency.

## Secondary comparisons: zero-heat-flux thermometer versus peripheral thermometers

Zero-heat-flux thermometers were compared with sublingual thermometers and nasopharyngeal thermometers in the studies included in this review. The mean bias between zero-heat-flux and sublingual temperature measurements in meta-analysis of results from `r SL$Studies` studies was `r SL$bias_mean` $^\circ C$. Due to the limited number of studies and measurements, population limits of agreement were extremely wide, spanning from `r SL$CI_L_rve` $^\circ C$ to `r SL$CI_U_rve` $^\circ C$. The quality of evidence for this comparison was rated as very low quality due to serious concerns about imprecision.

The mean bias between zero-heat-flux and nasopharyngeal temperature measurements in meta-analysis of results from `r NPA$Studies` studies was `r NPA$bias_mean` $^\circ C$. Population limits of agreement were `r NPA$CI_L_rve` $^\circ C$ to `r NPA$CI_U_rve` $^\circ C$. We downgraded the quality of evidence to low, again due to concerns about inconsistency and study limitations.

# Discussion

Results from this systematic review have important implications for practice. Clinicians should consider the potential that a temperature measurement from a zero-heat-flux thermometer could be as much as one $^\circ C$ higher or lower than the true core temperature. This is similar to results from previous meta-analyses that compared other peripheral thermometers with core temperature measurements. However, these previous meta-analyses used statistical approaches that did not incorporate the magnitude of heteroogeneity in results between studies or sampling error. As such, it is possible that the zero-heat-flux thermometer is still more precise than these other peripheral thermometers.

Whether or not teh zero-heat-flux thermometer is sufficiently accurate to be used in place of nasopharyngeal thermometers is unclear.

We did not include studies that used the Temple Touch Pro. This is a thermometer similar to the zero-heat-flux device in that it is placed cutaneously, but the underlying technology is different. There have been x studies that evaluated the Temple Touch Pro device with promising results.

## Limitations

# Conclusion

# References

>>>>

---
title: "Accuracy and precision of zero-heat-flux temperature monitoring"
description: A systematic review and meta-analysis
author: 
- name: Aaron Conway
  address: Peter Munk Cardiac Centre, UHN & Lawrence S. Bloomberg Faculty of Nursing, University of Toronto
  email: aaron.conway@utoronto.ca
  url: https://www.aaronconway.info
- name: Megan Bittner
  address: Lawrence S. Bloomberg Faculty of Nursing, University of Toronto
- name: Dan Phan
  address: Lawrence S. Bloomberg Faculty of Nursing, University of Toronto
- name: Navpreet Kamboj
  address: Lawrence S. Bloomberg Faculty of Nursing, University of Toronto
  email: navpreet.kamboj@mail.utoronto.ca
- name: Kristina Chang
  address: Toronto General Hospital, UHN
- name: Peter Collins
  address: Toronto General Hospital, UHN
- name: Matteo Parotto
  address: Toronto General Hospital, UHN
date: "`r Sys.Date()`"
bibliography: bibliography.bib
output: distill::distill_article
---

```{r echo=FALSE, include=FALSE}
library(tidyverse)
library(knitr)
library(bama) # https://github.com/awconway/bama
library(ggprisma) # https://github.com/awconway/ggprisma
library(gt)
```

```{r load-data, include=FALSE}
data <- readxl::read_xlsx(here::here("manuscript", "data", "zhf_extracted.xlsx"))
```

@@

<div class="l-page-outset">
<blockquote>
### Abstract

**Background**

Zero-heat-flux thermometers are non-invasive devices that can be used to continuously monitor temperature. These devices are increasingly being used in clinical practice to substitute for invasive core temperature measurement during surgery and in critical care settings. The aim of this review was to determine the accuracy and precision of zero-heat-flux temperture measurements.

**Methods**

Medline and EMBASE were searched for studies that reported on a measurement of core or peripheral temperature that coincided with a measurement from the zero-heat-flux device. Study selection and quality assessment (using the QUADAS-2) was performed independently. The GRADE approach was used to summarize the strength of the body of evidence.  Pooled estimates of the mean bias and limits of agreement with outer 95% confidence intervals (termed population limits of agreement) were calculated.

**Results**

Sixteen studies were included. The primary comparison of zero-heat-flux versus core temperature measurements consisted of `r primary$Comparisons` comparisons from `r primary$Studies` individual studies. Data from `r primary$Participants` participants with `r format(primary$Measurements, scientfic=F)` paired measurements were included. The pooled estimate for the mean bias was `r primary$bias_mean`°C. Population limits of agreement, which take into consideration the between-study heterogeneity and sampling error, were wide, spanning from `r primary$CI_L_rve`°C to `r primary$CI_U_rve`°C. The GRADE evidence quality rating was downgraded to moderate due to concerns about study limitations. Population limits of agreement for the sensitivity analysis restricted to studies rated as having low risk of bias across all the domains of the QADAS-2 were similar to the primary analysis.

**Conclusion**

The range of uncertainty in the accuracy of the zero-heat-flux thermometer should be taken into account when using measurements from this device to inform clinical decision-making. Clinicians should therefore consider the potential that a temperature measurement from a zero-heat-flux thermometer could be as much as 1°C higher or lower than core temperature. Use of this device may not be appropriate in situations where a difference in temperature of less than 1°C is important to detect.

</blockquote>
</div>

## Introduction

@@

## Methods

@@

### Inclusion criteria

@@

### Data sources and searches

Published studies were found by searching Medline and EMBASE from January 2000 to July 2019. The Cochrane-recommended search strategy combining terms for the ‘target condition’ and ‘index test’ was used [@mann2012should]. This search strategy is an efficient approach for systematic reviews of diagnostic test accuracy studies.[@preston2015improving] We also conducted forward citation searching, by using Google Scholar to search the citations of the first article published on the accuracy of zero-heat-flux thermometers. The search strategies used for each data base can be located [here](https://aconway.dev/zhf app). Selection of studies was undertaken independently by two reviewers using [Covidence](https://www.covidence.org).

### Data extraction and quality assessment

@@

### Data synthesis and analysis

@@

Measures of uncertainty were included in our meta-analyses by calculating the outer 95% confidence intervals for pooled limits of agreement. We also accounted for repeated measurements if they were not properly adjusted for in individual studies. This was achieved by using weights proportional to the number of participants, not the total number of measurements.  The R statistical program was used to conduct all analyses [@team2017r]. All data and R code used in the meta-analyses can be located [here](https://github.com/awconway/zhf-review).

Prior to conducting the meta-analyses, the results from each study were converted into a standard format, with bias meaning comparator thermometer minus ZHF thermometer measured in °C. In several studies, results were reported for multiple groups of participants, therefore in the meta-analysis each of these groups was treated as a separate 'comparison'. Other studies reported multiple sets of results, whereby analyses were conducted between ZHF and various comparator devices used on the same participant. These instances were also treated as a separate 'comparison' if the comparator devices were apart of separate meta-analyses groups. One study reported intraoperative, postoperative and overall results for the same participants. Only the paired measurements from the overall results were included in the main and low risk bias analyses, leaving paired measurements exclusively from the intraoperative and postoperative timepoints to be included in respective meta-analyses subgroups.

The conventionally cited clinically acceptable agreement between ZHF and comparator devices is 0.5 °C [@eshraghi2014]. It was deemed that outer confidence bounds for 95% LoA between zero-heat-flux and core temperature measurements (termed as ‘population limits of agreement’) outside of these bounds wouldbe clinically unacceptable.

A sensitivity analysis for the primary comparison (ZHF versus temperature measurement at core site) was performed based on risk of bias, whereby ‘unclear risk of bias’ was treated as ‘high risk’ and ‘high risk of bias’ studies were excluded from analyses. We also conducted a sensitivity analysis for the primary comparison (ZHF versus temperature measurement at core site) excluding studies that received funding from industry. As clinicians would be interested in the accuracy of ZHF relative within the clinical setting in which they use it, we conducted subgroup analyses for the primary comparison according to clinical setting of the study (either intraoperative or intensive care unit).

## Results

### Study selection and description

Sixteen studies were included (Figure \@ref(fig:fig-1)). Two studies reported only in abstract form were not included and assigned as 'studies awaiting classification' because there was insufficient information provided.

@@

The characteristics of included studies can be viewed [here](https://aconway.dev/zhf). The primary comparison of zero-heat-flux versus core temperature measurements (eg, arterial, bladder, esophageal or rectal) consisted of `r primary$Comparisons` comparisons from `r primary$Studies` individual studies. In total, data from `r primary$Participants` participants with `r format(primary$Measurements, scientfic=F)` paired measurements were included in this comparison (two studies did not report the total number of measurements included in their analysis). The sensitivity analysis for the primary comparison with only studies that were judged as low risk of bias across all domains included `r low_risk$Comparisons` comparisons from `r low_risk$Studies` studies that enrolled `r low_risk$Participants` participants with `r low_risk$Measurements` paired measurements (two studies did not report the total number of measurements included in their analysis). There were `r ICU$Studies` studies that compared zero-heat-flux to core temperature measurements in ICU patients, comprising `r ICU$Comparisons` comparisons with `r ICU$Measurements` measurements from `r ICU$Participants` participants. Another `r OT$Studies` studies were included that compared zero-heat-flux to core temperature measurements in patients undergoing surgery, comprising `r OT$Comparisons` comparisons with `r OT$Measurements` measurements from `r OT$Participants` participants. Nasopharyngeal thermometers were used as the comparator devices in `r NPA$Studies` studies, with `r NPA$Measurements` paired measurements from `r NPA$Measurements` participants. Sublingual thermometers were used as the comparator devices in `r SL$Studies` studies that reported `r SL$Measurements` paired measurements from `r SL$Participants` participants.

@@

### Primary comparison: zero-heat-flux thermometer versus core thermometers

A graphical overview of the findings for the primary analysis is presented in Figure \@ref(fig:fig-2). The pooled estimate for the mean bias between zero-heat-flux and core temperature measurements was `r primary$bias_mean`°C. The population limits of agreement, which take into consideration the between-study heterogeneity and sampling error, were wide, spanning from `r primary$CI_L_rve`°C to `r primary$CI_U_rve`°C (`r primary$Measurements` measurements; `r primary$Participants` participants; `r primary$Studies` studies). The quality of evidence for the primary comparison was downgraded to low quality due to concerns about study limitations and inconsistency. Population limits of agreement for the sensitivity analysis restricted to studies rated as having low risk of bias across all the domains of the QADAS-2 were similar to the primary analysis (`r low_risk$Measurements` measurements; `r low_risk$Participants` participants; `r low_risk$Studies` stsudies). The mean bias was again `r low_risk$bias_mean`°C with population limits of agreement spanning from `r low_risk$CI_L_rve`°C to `r low_risk$CI_U_rve`°C. A further sensitivity analysis excluding studies that received industry funding revealed population limits of agreement that were considerably wider than the primary analysis (`r conflict$CI_L_rve`°C to `r conflict$CI_U_rve`°C). The GRADE rating for this sensitivity was downgraded to low quality though, due to concerns about study limitations, inconsistency and imprecision.

<div class="l-screen-inset">

```{r fig-2, fig.align="center", fig.cap="Graphical overview of findings for the primary analysis", echo=FALSE, fig.path=""}
include_graphics("gofer_core.png")
```

</div>

Table 1 presents results of the primary, sensitivity and all subgroup analyses for the primary comparison as well as secondary comparisons. We conducted two subgroup analyses for the primary comparison according to the clinical setting in which the study was conducted. In the subset of studies conducted in the ICU, the mean bias was `r ICU$bias_mean`°C with population limits of agreement between `r ICU$CI_L_rve`°C and `r ICU$CI_U_rve` °C. The GRADE rating for quality of evidence was downgraded to very low quality due to study limitations, inconsistency and imprecision. In the subset of studies that evaluated the use of zero-heat-flux thermometers during surgery found a mean bias of `r OT$bias_mean`°C with population limits of agreement from `r OT$CI_L_rve`°C to `r OT$CI_U_rve` °C. The quality of evidence rated as moderate quality due to concerns about study limitations.

<div class="l-page-outset">

```{r table-1}
ma <- list(primary, low_risk, ICU, OT,  NPA,SL, conflict)
names(ma) <- c("Primary", "Low risk studies", "Intensive Care Unit", 
               "Surgery", "Nasopharyngeal", "Sublingual",
               "Studies not funded by industry")
df <- bind_rows(ma, .id="Comparison")
df %>% 
  rename("Mean bias" = bias_mean, "Variance" = sd2_est, "Tau-squared" = tau_est, "Lower bound for 95% limit of agreement" = LOA_L, "Upper bound for 95% limits of agreement" = LOA_U, "Outer confidence interval for lower 95% limits of agreement" = CI_L_rve, "Outer confidence interval for upper 95% limits of agreement" = CI_U_rve) %>% 
    gt() %>% 
  tab_header(
    title = "Table 1. Results of meta-analyses"  )  %>% 
  tab_spanner(
    label = "Population limits of agreement",
    columns = vars(
      `Outer confidence interval for lower 95% limits of agreement`, `Outer confidence interval for upper 95% limits of agreement`)
  )
```
</div>

### Secondary comparisons: zero-heat-flux thermometer versus peripheral thermometers

Zero-heat-flux thermometers were compared with sublingual thermometers and nasopharyngeal thermometers in the studies included in this review. The mean bias between zero-heat-flux and sublingual temperature measurements in meta-analysis of results from `r SL$Studies` studies was `r SL$bias_mean`°C. Due to the limited number of studies and measurements, population limits of agreement were extremely wide, spanning from `r SL$CI_L_rve`°C to `r SL$CI_U_rve`°C. The quality of evidence for this comparison was rated as very low quality due to serious concerns about imprecision.

The mean bias between zero-heat-flux and nasopharyngeal temperature measurements in meta-analysis of results from `r NPA$Studies` studies was `r NPA$bias_mean` °C. Population limits of agreement were `r NPA$CI_L_rve`°C to `r NPA$CI_U_rve`°C. We downgraded the quality of evidence to low, again due to concerns about imprecision and study limitations.

## Discussion

Results from this systematic review have important implications for practice. Clinicians should consider the potential that a temperature measurement from a zero-heat-flux thermometer could be as much as one degree Celcius higher or lower than core temperature. It was reassuting that results of our sensitivity analysis restricted to studies judged to be at low risk of bias using the QADAS-2 tool were similar. As such, it is vital for clinicians considering using this device to first determine if differences in temperature smaller than this magnitude would be important for the given clinical situation. If so, then it may not be appropriate to substitute the zero-heat-flux device in place of a core thermometer.

Our estimates of the accuracy of zero-heat-flux thermometers are similar to results from a previous meta-analysis that compared other peripheral thermometers, such as sublingual and temporal artery devices, with core temperature measurements [@niven2015accuracy]. However, this previous meta-analysis used a statistical approach that did not incorporate the magnitude of heteroogeneity in results between studies or sampling error. As such, it is possible that the zero-heat-flux thermometer may still more precise than other peripheral thermometers.

Subgroup analyses revealed insights to direct future research. There were fewer participants included in the subgroup of studies conducted in the Intensive Care Unit compared to those conducted during surgery. As a result, population limits of agreement for the Intensive Care Unit subgroup were broad. Additional studies are required to increase confidence in the accuracy of zero-heat-flux device in this setting, where continuous temperature monitoring is often required.

Although comparisons with core temperture are the most important to evaluate, we included studies that compared zero heat flux and peripheral temperature monitoring devices in our review because clinicians may be interested to determine if this new technology is sufficiently accurate to replace other ways non-invasive monitor temperature. Also, there may be situations where it is not practical to expose research participants to the potential additional risk of invasive core temperature monitoring for the purposes of evaluating the new temperature monitoring device when it is standard practice for only peripheral temperature monitoring to be used. Whether or not the zero-heat-flux thermometer is sufficiently accurate to be used in place of nasopharyngeal thermometers is unclear. Population limits of agreement calculated from four studies were broad, spanning from one degree less than zero heat flux temperature to one degree higher. Further studies are therefore required.

It should be noted that we did not include studies that used the Temple Touch Pro because it is not strictly a zero-heat-flux device. This is a new thermometer that is similar to the zero-heat-flux device in that it is placed cutaneously, but the underlying technology is different. Far fewer studies have  evaluated the Temple Touch Pro compared to the zero-heat-flux device [@evron2017evaluation; @sastre2019evaluation].

Many studies in this review analysed a large number of measurements of temperature with relatively small sample sizes. Importantly, the approach we used for our meta-analysis takes this into account. By using robust variance estimation, weights for pooling estimates in the meta-analyis become proportional to the number of patients not the total number of measurements.[@tipton2017framework]

The accuracy of zero heat flux temperature monitoring has been evaluated in various intra-operative contexts as well as in the intensive care unit setting. Our subgroup analyses did not indicate that the accuracy of this temperature monitoring device was any more effective in a particular setting. Only one study included in our systematic review included pediatric patients. Additional studies to evaluate the accuracy of this device in children may be warranted to increase confidence.

### Limitations

We did not extract data on adverse events due to zero-heat-flux temperature monitoring. The possibility of publication bias cannot be ruled out, although the evidence suggests this may not be as serious of a problem for studies that are not randomized controlled trials [@begg2005systematic]. Our focus for the meta-analysis was on calculating population limits of agreement, which incorporate the variation in bias between studies into the estimates. For this reason, we did not use meta-regression or tests for interaction between subgroups as a way to investigate sources of heterogeneity. It is important to note that this review did not assess the clinical utility of temperature monitoring using the zero-heat-flux device. The evidence from this review should be considered in the context of other information about the reliability and ease of use of this device.

## Conclusion

Substantial differences between core and zero-heat-flux temperature measurements were identified in this meta-analysis. Clinicians should consider the range of uncertainty in the accuracy of the zero-heat-flux thermometer when using this device to inform their decision-making. As such, there may be circumstances where use of this device would not be appropriate because a difference in temperature of 1°C is important to detect for the given clinical situation.
